/---
title: "Homework 01"
---


## TidyTuesday Part

Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story mainly composed of [effective visualizations](https://docs.google.com/presentation/d/1WHr6Itzm2IJLxvppcacxHpr8R4NxO4MfvWWUPmtQx6Q/preview?slide=id.g13360dab5d5_0_61).  Provide sufficient background for readers to grasp your narrative.  Refer to the Homework Instructions ⭐ page on the course website for details on how to submit this part.
```{r}
install.packages(c("sf","elevatr","terra","stars","tidycensus"))

install.packages('devtools')
devtools::install_github("ropensci/USAboundaries")
install.packages("USAboundariesData", repos = "https://ropensci.r-universe.dev", type = "source")
```

Research Question: How does geographic area affect the price of a cappuccino?

```{r}
tuesdata <- tidytuesdayR::tt_load('2026-09-08')
cafe <- tuesdata$cafe
```

Wrangling: Creating 'Area' Variable

```{r}
cafe <- cafe |>
  mutate(area = if_else(urban == TRUE, "urban", 
                        if_else(suburban == TRUE, "suburban", 
                                if_else(rural == TRUE, "rural", NA))))
```


Visualization 1: 

```{r}
cafe |>
  filter(country == "USA") |>
  ggplot(aes(x = area, y = price)) +
    geom_boxplot()
```

